Comparing ChatGPT-4 to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6939 Deaths in Sierra Leone from 2019-2022

### 2024-02-07 manuscript/manuscript.tex
Add top_p justification

The parameter \verb|top_p| for ChatGPT-3.5 and ChatGPT-4, representing the sampling temperature, was set to 0.3 to consider only the top 30\% probability mass from the token results \cite{openaiOpenAIPlatformAPI2024}. Higher values closer to 1 may make the results more random, while lower values closer to 0 make the results more focused. The \verb|Nsim| (number of iterations to run) parameter \cite{liInSilicoVAProbabilisticVerbal2022} for InSilicoVA was set to 9500\footnote{The default value of Nsim=10000 for InSilicoVA ran until 9500 iterations before it stopped due to errors, thus Nsim=9500 was used and ran successfully for all iterations.}, while the \verb|HIV| (level of prevalence of human immunodeficiency virus) and \verb|Malaria| (level of prevalence of Malaria) parameters \cite{thomasInterVA5ReplicateAnalyse2021} for InterVA-5 were both set to \verb|'h'| (high) reflecting HIV and Malaria disease assumptions in Sierra Leone \cite{yendewaHIVAIDSSierra2018,walkerMalariaMorbidityMortality2015}.

>>>>

The parameter \verb|top_p| for ChatGPT-3.5 and ChatGPT-4, representing the sampling temperature, was set to 0.3\footnote{We tested for top\_p values between 0.1 to 0.9 at intervals of 0.1 on five records that did not return outputs from ChatGPT-4 until all five records returned output. At top\_p=0.3, all five records produced output.} to consider only the top 30\% probability mass from the token results \cite{openaiOpenAIPlatformAPI2024}. Higher values closer to 1 may make the results more random, while lower values closer to 0 make the results more focused. The \verb|Nsim| (number of iterations to run) parameter \cite{liInSilicoVAProbabilisticVerbal2022} for InSilicoVA was set to 9500\footnote{The default value of Nsim=10000 for InSilicoVA ran until 9500 iterations before it stopped due to errors, thus Nsim=9500 was used and ran successfully for all iterations.}, while the \verb|HIV| (level of prevalence of human immunodeficiency virus) and \verb|Malaria| (level of prevalence of Malaria) parameters \cite{thomasInterVA5ReplicateAnalyse2021} for InterVA-5 were both set to \verb|'h'| (high) reflecting HIV and Malaria disease assumptions in Sierra Leone \cite{yendewaHIVAIDSSierra2018,walkerMalariaMorbidityMortality2015}.
